---
title: "How to use those functions"
author: "Hector Roux de Bézieux"
date: '`r format(Sys.time(), "%d %B , %Y")`'
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
vignette: >
  %\VignetteIndexEntry{'Vignette for **tradeSeq**}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r packages, include=F}
library(knitr)
opts_chunk$set(
  fig.pos = "!h", out.extra = "", warning = F, message = F,
  fig.width = 5, fig.align = "center"
)
libs <- c("DailyHRB", "ggplot2")
suppressMessages(
  suppressWarnings(sapply(libs, require, character.only = TRUE))
)
rm(libs)
```

# Installation

You can install this pacakge from Github using
```{r, eval = F}
if (!"devtools" %in% installed.packages()) {
  install.pacakges("devtools")
}
devtools::install_github("HectorRDB/DailyHRB")
```

Alternatively, you can download it from Github and build it from source.
```{bash, eval = F}
git clone git@github.com:HectorRDB/DailyHRB.git
R CMD INSTALL DailyHRB
```

# Templates

This package provide two templates that I regularly use. Templates are an *[RStudio](https://www.rstudio.com/)* functionality that I find very useful to speed up project creation. To use those templates, install the package then open RStudio.

- __Rmd template__: Click on _New File_ (or the "+" button), select _R Markdown..._ in the pulldown menu. Then, select _From Template_ and select _My Template (DailyHRB)_.
- __Project Template__: Click on _New Project (or the second "+" button), select _New Project_. Then, select _Personal Project Template_.

To create similar files for yourself, the easiest way is to create your own package. Then, create a __Rmd__ file that you want as template and create a struture similar to the [__int__ folder of the Github repo](https://github.com/HectorRDB/DailyHRB/tree/master/inst). 

For the project, it ia bit more complex. It relies on the *[project.R](https://github.com/HectorRDB/DailyHRB/blob/master/R/project.R)* file in the __R__ folder and some other files in [__inst__](https://github.com/HectorRDB/DailyHRB/tree/master/inst). I hope to be able to create a tutorial at some point.

# Functions
## my_theme

I rely a lot on *ggplot2* to quickly plot nice graphs but I don't like the deaults themes. The one I prefer is the *theme_classic* but it still needed some improvements. So I build a *ggplot2* theme.

```{r}
p <- ggplot(data.frame(x = 0:10, y = 0:10 + rnorm(11)),
       aes(x = x, y = y)) +
  geom_point()
p 
p + my_theme()
```

## ipak

This function loads the packages and install them from CRAN or Bioconductor if needed, using the [__BiocManager__](https://cran.r-project.org/web/packages/BiocManager/index.html) package.

```{r}
# Example
ipak(c("ggplot2", "Biobase"))
```

## checkType

This function is useful when analyzing micro-array data, RNA-Seq or scRNA-Seq data. It plots the boxplot of 10 (tunable) random columns from the input matrix. It allows to quickly see whether the data is logged and / or normalized when exploring a new dataset.

```{r}
data <- matrix(rnbinom(1000 * 100, size = 1000, prob = .999), ncol = 100)
checkType(data)
```

## Clean

It is a function that I use to clean metadata file, typically from [SRA](https://www.ncbi.nlm.nih.gov/sra). It removes all columns that only have one unique value, and optionaly all columns that have no value with duplicates.

```{r}
metaData <- data.frame(SRA = "SRA17CJQ1",
                       ID1 = sample(letters, 12, replace = F),
                       group = c(rep("group1", 4), rep("group2", 4), rep("group3", 4)))
metaData$ID2 <- toupper(metaData$ID1)
metaData
clean(metaData)
clean(metaData, unique = F, keep = "ID1")
```

## plotSmiley

A sily function I did once when I was bored

```{r}
plotSmiley()
```

## colors

Just a shorcut, `colors()` is equivalent to `RColorBrewer::display.brewer.all()`. Setting *print = TRUE* will also print the names of all palettes in RColorBrewer. 
